---
title: "Pollinators_Aristolochia"
output: html_document
date: "2024-03-11"
---

#Packages
```{r include=FALSE}
vapply(c("magrittr","stringr", "readr", "scales", "mgcv", "RColorBrewer", "dplyr","ggplot2","car","tidyverse", "lme4", "vegan", "grid","emmeans","ggmap","mvabund","cowplot","ggpubr","ggpattern","lubridate"), library, logical(1L),
       character.only = TRUE, logical.return = TRUE)
citation(package = "lme4")

library("remotes")
#remotes::install_github("coolbutuseless/ggpattern")
```

#Import data
```{r}
#Pollinators
data.poll.mtp<-read.csv("D2_Data_pollinators.csv",header = T, row.names = NULL,sep = ";")

#Flowers inspected
data.inspect<-read.csv("D3_Data_sessions_flowers_counted.csv",header = T, row.names = NULL,sep = ";")
```

#Warning: change "collection_date (yyyy-mm-dd)" by "date"

#Date
```{r}
data.poll.mtp$date<-gsub("/","-",data.poll.mtp$date)
data.poll.mtp$date<-dmy(data.poll.mtp$date)
str(data.poll.mtp$date)

data.inspect.mtp$date<-gsub("/","-",data.inspect.mtp$date)

#Warning to date format
data.inspect.mtp$date<-dmy(data.inspect.mtp$date)
str(data.inspect.mtp$date)
```

#Pool data on flowers inspected by species x date x station
```{r}
data.inspect.mtpM<-aggregate(data.inspect.mtp$nb_flowers_inspected, by=list(data.inspect.mtp$date,data.inspect.mtp$locality_code,data.inspect.mtp$plant_species), FUN=sum)
colnames(data.inspect.mtpM)<-c("date","locality_code","plant_species","nb_flowers_inspected")
```

#Extract pollinating species of Aristolochia species
```{r}
list.poll <- filter(data.poll.mtp, species != "", plant_species %in% c("Aristolochia rotunda", "Aristolochia pistolochia", "Aristolochia clematitis"), statut=="pollinator") %>% distinct(species) %>% pull(species)
list.poll<-as.factor(list.poll)
list.poll<-droplevels(list.poll)

list.poll.rot <- filter(data.poll.mtp, statut == "pollinator", species != "", plant_species %in% c("Aristolochia rotunda")) %>% distinct(species) %>% pull(species)
list.poll.pis <- filter(data.poll.mtp, statut == "pollinator", species != "", plant_species %in% c("Aristolochia pistolochia")) %>% distinct(species) %>% pull(species)
list.poll.cle <- filter(data.poll.mtp, statut == "pollinator", species != "", plant_species %in% c("Aristolochia clematitis")) %>% distinct(species) %>% pull(species)
```

***************************************************************************************************
*Identity of floral visitors*
***************************************************************************************************

#Number of flowers occupied
```{r}
length(unique(data.poll.mtp$flower_code[data.poll.mtp$plant_species=="Aristolochia rotunda"]))
length(unique(data.poll.mtp$flower_code[data.poll.mtp$plant_species=="Aristolochia rotunda" & data.poll.mtp$nb_individuals>0]))

length(unique(data.poll.mtp$flower_code[data.poll.mtp$plant_species=="Aristolochia pistolochia"]))
length(unique(data.poll.mtp$flower_code[data.poll.mtp$plant_species=="Aristolochia pistolochia" & data.poll.mtp$nb_individuals>0]))

length(unique(data.poll.mtp$flower_code[data.poll.mtp$plant_species=="Aristolochia clematitis"]))
length(unique(data.poll.mtp$flower_code[data.poll.mtp$plant_species=="Aristolochia clematitis" & data.poll.mtp$nb_individuals>0]))
```

#Pollen carriers
```{r}
data.poll.mtp$statut<-as.factor(data.poll.mtp$statut)
list.porteur <- filter(data.poll.mtp, species != "", plant_species %in% c("Aristolochia rotunda", "Aristolochia pistolochia", "Aristolochia clematitis"), statut %in% c("pollinator","pollen_carrier")) %>% distinct(species) %>% pull(species)
list.porteur<-as.factor(list.porteur)
list.porteur<-droplevels(list.porteur)

list.porteur.rot <- filter(data.poll.mtp, statut %in% c("pollinator","pollen carrier"), species != "", plant_species %in% c("Aristolochia rotunda")) %>% distinct(species) %>% pull(species)
list.porteur.pis <- filter(data.poll.mtp, statut %in% c("pollinator","pollen carrier"), species != "", plant_species %in% c("Aristolochia pistolochia")) %>% distinct(species) %>% pull(species)
list.porteur.cle <- filter(data.poll.mtp, statut %in% c("pollinator","pollen carrier"), species != "", plant_species %in% c("Aristolochia clematitis")) %>% distinct(species) %>% pull(species)
```

#Pollinators
```{r}
polli<-subset(data.poll.mtp, data.poll.mtp$statut=="pollinators")
polli[is.na(polli)] <- 0
Arot<-subset(polli, polli$plant_species=="Aristolochia rotunda")
Apis<-subset(polli, polli$plant_species=="Aristolochia pistolochia")
Aclem<-subset(polli, polli$plant_species=="Aristolochia clematitis")
```

```{r}
Arotn<-Arot %>% group_by(species) %>% summarise(nb = sum(nb_individuals))
Apisn<-Apis %>% group_by(species) %>% summarise(nb = sum(nb_individuals))
Aclemn<-Aclem %>% group_by(species) %>% summarise(nb = sum(nb_individuals))

Arotn$plant<-rep("Aristolochia rotunda", nrow(Arotn))
Apisn$plant<-rep("Aristolochia pistolochia", nrow(Apisn))
Aclemn$plant<-rep("Aristolochia clematitis", nrow(Aclemn))

plant<-bind_rows(Arotn,Apisn)
plant<-bind_rows(plant,Aclemn)
b<-select(polli,family,genus,species)
b<-unique(b)
plant2<-left_join(b,plant,by="species")

plant2<-tibble(plant2)
```

```{r}
data.poll.male<-subset(data.poll.mtp, statut=="pollinator" & sex=="M")
```

#Visits of pollinating species
```{r}
insectf<-filter(data.poll.mtp, sex %in% c("F"))
insectm<-filter(data.poll.mtp, sex %in% c("M"))

#A.rotunda
Rotundan<-subset(insectf,insectf$plant_species=="Aristolochia rotunda")
rot<- Rotundan %>% group_by(species) %>% summarise (sum(nb_individuals))
rot$plant<-rep("Aristolochia rotunda",nrow(rot))

#A.pistolochia
Pistolochian<-subset(insectf,insectf$plant_species=="Aristolochia pistolochia")
pis<- Pistolochian %>% group_by(species) %>% summarise (sum(nb_individuals))
pis$plant<-rep("Aristolochia pistolochia",nrow(pis))

#A.clematitis
Clematitisn<-subset(insectf,insectf$plant_species=="Aristolochia clematitis")
clem<- Clematitisn %>% group_by(species) %>% summarise (sum(nb_individuals))
clem$plant<-rep("Aristolochia clematitis",nrow(clem))

Tabvisit<-bind_rows(rot,pis)
Tabvisit<-bind_rows(Tabvisit,clem)
Tabvisit

Tabvisit<-tibble(Tabvisit)
```

#Pollen load for each species

>Warning: verify if there is pollen on different individuals/species on the same flower to avoid counting twice pollen deposited on stigma

#A. clematitis
```{r}
Aclem2<-aggregate(Aclem$nb_pollen_insect, by=list(Aclem$species, Aclem$flower_code,Aclem$nb_pollen_stigmate, Aclem$nb_individuals), sum)
colnames(Aclem2)<-c("species","flower_code","nb_pollen_stigmate","nb_individuals","nb_pollen_insect")
Aclem2$pollen<-(Aclem2$nb_pollen_stigmate+Aclem2$nb_pollen_insect)
tapply(Aclem2$pollen, Aclem2$species, sum)
```

#A. pistolochia
```{r}
Apis2<-aggregate(Apis$nb_pollen_insect, by=list(Apis$species, Apis$flower_code,Apis$nb_pollen_stigmate, Apis$nb_individuals), sum)
colnames(Apis2)<-c("species","flower_code","nb_pollen_stigmate","nb_individuals","nb_pollen_insect")
Apis2$pollen<-(Apis2$nb_pollen_stigmate+Apis2$nb_pollen_insect)
tapply(Apis2$pollen, Apis2$species, sum)
```

#A. rotunda
```{r}
Arot2<-aggregate(Arot$nb_pollen_insect, by=list(Arot$species, Arot$flower_code,Arot$nb_pollen_stigmate, Arot$nb_individuals), sum)
colnames(Arot2)<-c("species","flower_code","nb_pollen_stigmate","nb_individuals","nb_pollen_insect")
Arot2$pollen<-(Arot2$nb_pollen_stigmate+Arot2$nb_pollen_insect)
tapply(Arot2$pollen, Arot2$species, sum)
```


*Binomials tests for sex-ratio*

>Example for one species

```{r}
Faris<-c(9,0)
binom.test(Faris,p=0.5,alternative="greater",conf.level=0.95) #pvalue=2.23e-13 ***
```

#Number of males for each pollinator species in each Aristolochia species
```{r}
#clematitis
MaleClem<-subset(Clematitisn, Clematitisn$sex=="M")
MaleClem<-aggregate(MaleClem$n_individuals, by=list(MaleClem$species), sum)
 
#pistolochia
MalePis<-subset(Pistolochian, Pistolochian$sex=="M")
MalePis<-aggregate(MalePis$nb_individuals, by=list(MalePis$species), sum)

#rotunda
MaleRot<-subset(Rotundan, Rotundan$sex=="M")
MaleRot<-aggregate(MaleRot$nb_individuals, by=list(MaleRot$species), sum)
```

********************************************************************************
*Factors of variation in pollinator communities*
********************************************************************************

*Abundance matrix of pollinating species of the three Aristolochia species*
This matrix is formatted as 'vegan' (rows = flowers, columns = pollinators) and contains all the pollinating species (not separated by species of Aristolochia)

```{r}
data.poll.sstr <- filter(flower_code != "") %>% 
  select(flower_code, species, nb_individuals) %>% arrange(flower_code) %>% #
  pivot_wider(names_from = species, values_from = nb_individuals, values_fill = 0, values_fn = sum) %>% 
  left_join(select(data.poll.mtp, date, year, month, locality_code,latitude, longitude, plant_species, flower_code), by="flower_code") %>%
  distinct(flower_code, .keep_all = TRUE)
data.poll.sstr<-droplevels(data.poll.sstr)
```

*Pollinator communities with pooled data by station x date x plante_species*

```{r}
library(dplyr)
#TOUT
data.poll.station.date <- filter(data.poll.mtp, species %in% list.poll) %>% group_by(date, locality_code, plant_species, species) %>% summarise(n=sum(nb_individuals)) %>% ungroup() %>% pivot_wider(names_from = species, values_from = n, values_fill = 0, values_fn = sum) %>%
  left_join(select(data.poll.mtp, date, year, month, locality_code, plant_species), by=c("date", "locality_code", "plant_species")) %>%
  distinct(date, locality_code, plant_species, .keep_all = TRUE) 
```

*Models manyGLM*
```{r}
library("mvabund")
# Multivariate glm
data.poll.station.date.DV <- mvabund(select(data.poll.station.date, all_of(list.poll))) 

glm.poll <- manyglm(data.poll.station.date.DV~plant_species+locality_code+month, data=data.poll.station.date, family="negative_binomial")
```

```{r}
sum.glm.poll<-summary.manyglm(glm.poll,resamp="residual",show.time="total")
sum.glm.poll

ano.glm.poll<-anova.manyglm(glm.poll,show.time="total")
ano.glm.poll
```

```{r}
#Test residuals
library(mvabund)
library(DHARMa)
residuals(glm.poll)
plot(glm.poll)
plot(glm.poll, which=1)
plot(glm.poll, which=2)
plot(glm.poll, which=3)

simulateResiduals(glm.poll, refit=T)
testZeroInflation(simulateResiduals(glm.poll, refit=T))
```

*Supplementary figure geographical effect*
```{r}
data_subset<-select(data.poll.mtp,species,nb_individuals,date,locality_code,plant_species)
data_subset<-filter(data_subset, species %in% list.poll)
data_subset<-tibble(data_subset)

data_subset2<- aggregate(data_subset$nb_individuals, by=list(data_subset$species,data_subset$locality_code,data_subset$plant_species), FUN=sum)
colnames(data_subset2)<-c("species","locality_code","plant_species","nb_individuals")

data_subset3<-filter(data_subset2, species %in% c("Tricimba cincta", "Tricimba humeralis", "Chloropidae spChloro12","Conioscinella cf mimula", "Hapleginella laevifrons","Polyodaspis ruficornis"))
library(Hmisc)
data_subset2<- filter(data_subset2, species %nin% c("Tricimba cincta", "Tricimba humeralis", "Chloropidae spChloro12","Conioscinella cf mimula", "Hapleginella laevifrons","Polyodaspis ruficornis"))
data_subset3<-aggregate(data_subset3$nb_individuals, by=list(data_subset3$locality_code,data_subset3$plant_species), sum)
data_subset3$species<-rep("Other Cloropidae species", nrow(data_subset3))
colnames(data_subset3)<-c("locality_code","plant_species","nb_individuals","species")

data_subset4<-union(data_subset2,data_subset3)
```

```{r}
data.inspect.subset2<-select(data.inspect.mtpM,locality_code,plant_species, nb_flowers_inspected)
data.inspect.subset2<- aggregate(data.inspect.subset2$nb_flowers_inspected, by=list(data.inspect.subset2$locality_code,data.inspect.subset2$plant_species), FUN=sum)
colnames(data.inspect.subset2)<-c("locality_code","plant_species","nb_flowers_inspected")

data_freq_mtp<-inner_join(data_subset4,data.inspect.subset2, by=c("locality_code","plant_species"))
data_freq_mtp$prob<-data_freq_mtp$nb_individuals/data_freq_mtp$nb_flowers_inspected
```

```{r}
library(dplyr)
library(ggplot2)
factors <- c("ML1", "SG3","SJC1","ES1","MA1","ME1","SA1","VA1","BR1","BR2","PU2","SG1","VF2","VL1","PO1","LAM1","SG11","MU1","PU1","SG2","SG5")

data_freq_mtp$species <- factor(data_freq_mtp$species, levels = c("Dasyhelea punctiventris","Dasyhelea turficola","Forcipomyia alacris", "Forcipomyia aristolochiae","Forcipomyia knockensis","Forcipomyia monilicornis","Forcipomyia psilonota","Forcipomyia spCerato10","Trachysiphonella ruficeps","Other Cloropidae species"))

data_freq_mtp %>% filter(nb_flowers_inspected >100)  %>%
 ggplot() +
 aes(x = locality_code, y = prob, fill = species) +
 geom_col() + scale_y_continuous(trans = "log1p") +
 theme(axis.text.y = element_text(face = "bold"), axis.text.x = element_text(face = "bold", angle = 13L),axis.title.x = element_text(size = 14, face = "bold"), axis.title.y = element_text(size = 14, face = "bold")) +
 scale_fill_manual(values= c("#C0CA33","#336666","#FFFF00","#FFCC00","#FF6600","#FF3399","#990099","#9900FF","#3399FF","#009")) +
 labs(x = "Station", y = "Pollinating species/flower") + geom_text(aes(label = nb_flowers_inspected),position = position_stack(vjust = 0.5))+
 facet_wrap(vars(plant_species),scales = "free_y", ncol = 1L) + theme_light() + scale_x_discrete(limits = factors)
```

*Supplementary figure temporal effect*
**Pollinators collected**
```{r}
library(dplyr)
library(ggplot2)
library(lubridate)

temporal<-filter(data.poll.mtp, species %in% list.poll)
temporalbis<-temporal
year(temporal$date)<-2021 #only for figure display
temporal<-filter(temporal, temporal$flower_code!="")
temporal2<-aggregate(temporal$nb_individuals, by=list(temporal$species,temporal$date, temporal$plant_species), sum)
colnames(temporal2)<-c("species","date","plant_species","nb_individuals")

temporalp<-filter(temporal2, species %in% c("Tricimba cincta", "Tricimba humeralis", "Chloropidae spChloro12","Conioscinella cf mimula", "Hapleginella laevifrons","Polyodaspis ruficornis"))
library(Hmisc)
temporal2<- filter(temporal2, species %nin% c("Tricimba cincta", "Tricimba humeralis", "Chloropidae spChloro12","Conioscinella cf mimula", "Hapleginella laevifrons","Polyodaspis ruficornis"))
temporalp<-aggregate(temporalp$nb_individuals, by=list(temporalp$date,temporalp$plant_species), sum)
temporalp$species<-rep("Other Cloropidae species", nrow(temporalp))
colnames(temporalp)<-c("date","plant_species","nb_individuals","species")

temporal2p<-union(temporal2,temporalp)

temporal3<-aggregate(temporal$nb_individuals, by=list(temporal$date, temporal$plant_species), sum)
colnames(temporal3)<-c("date","plant_species","total")
temporal4<-full_join(temporal2p,temporal3, by=c("date","plant_species"))
temporal4$freq<-temporal4$nb_individuals/temporal4$total
```

```{r}
library(ggplot2)
library(ggbreak)

temporal4$species <- factor(temporal4$species, levels = c("Dasyhelea punctiventris","Dasyhelea turficola","Forcipomyia alacris", "Forcipomyia aristolochiae","Forcipomyia knockensis","Forcipomyia monilicornis","Forcipomyia psilonota","Forcipomyia spCerato10","Trachysiphonella ruficeps","Other Cloropidae species"))

temporal4 %>% filter(date >= "2021-01-01" & date <= "2021-11-01") %>%
ggplot () +
 aes(x = date, y = freq, fill = species) +
 geom_bar(stat = "summary", fun = "sum") +
 scale_fill_manual(values= c("#C0CA33","#336666","#FFFF00","#FFCC00","#FF6600","#FF3399","#990099","#9900FF","#3399FF","#009"))+ scale_x_break(c("2021-06-20", "2021-09-20")) + theme(axis.text.x = element_text(face = "bold", size = 7L)) + scale_x_date(date_labels = "%B") +  labs(x = "Season", y = "Frequence of pollinating species") + facet_wrap(vars(plant_species),scales = "free_y" ,nrow = 3L)+ theme_light()
```

**Number of flowers inspected**
```{r}
library(ggplot2)

temporalcount<-data.inspect.mtpM
temporalbiscount<-temporalcount
year(temporalcount$date)<-2021 #only for figure display
```

```{r}
temporalcount %>% filter(date >= "2021-02-27" & date <= "2021-11-01") %>%
ggplot () +
 aes(x = date, y = nb_flowers_inspected, fill = plant_species) +
 geom_smooth(se = F, colour= "black", n = 250, linewidth = 0.5) + scale_x_break(c("2021-06-20", "2021-09-20")) + theme(axis.text.x = element_text(face = "bold", size = 7L)) + scale_x_date(date_labels = "%B", limits= as.Date(c("2021-02-27", "2021-11-01"))) +  labs(x = "Season", y = "Number of flowers inspected") + facet_wrap(vars(plant_species),scales = "free_y" ,nrow = 3L) + theme_light()
```

*Sampling efforts on the data subset where flowers inspected were counted*
```{r warning=FALSE}
data.inspect.mtp %>% group_by(plant_species) %>% summarise(nb_insp=sum(nb_flowers_inspected))
```

*List of stations, plant species assemblages and GPS coordinates*
```{r}
list.stationsbis <- data.poll.mtp %>% distinct(locality_code, plant_species) %>% count(locality_code) %>%
  mutate(pop_type = if_else(n==1, "pure", "mixte"))
list.stationsbis

list.stationsbis %>%
  count(pop_type)

stationsGIS2 <- data.inspect.mtp %>% select(locality_code, latitude, longitude) %>% distinct(locality_code, .keep_all=T)
```

*Mantel test*
```{r}
list.stations2<-stationsGIS2
list.stations2<-tibble(list.stations2)
list.stations2<- list.stations2  %>% relocate(latitude, .after = longitude)

library(sp)
library(dplyr)
library(vegan)
library(geosphere)
```

*Aristolochia rotunda*
```{r}
data.poll.flower.rotunda <- filter(data.poll.mtp,plant_species %in% c("Aristolochia rotunda")) %>% 
  filter(flower_code != "") %>%
  select(flower_code, species, nb_individuals) %>% arrange(flower_code) %>%
  pivot_wider(names_from = species, values_from = nb_individuals, values_fill = 0, values_fn = sum) %>% 
  left_join(select(data.poll.mtp,locality_code, latitude, longitude, flower_code), by="flower_code") %>% #
  distinct(flower_code, .keep_all = TRUE)

data.poll.flower.rotunda<-droplevels(data.poll.flower.rotunda)

#geographic data frame - haversine distance
geo_rotunda2 = data.frame(data.poll.flower.rotunda$longitude, data.poll.flower.rotunda$latitude)

geo_rotunda2$data.poll.flower.rotunda.longitude<-as.numeric(geo_rotunda2$data.poll.flower.rotunda.longitude)
geo_rotunda2$data.poll.flower.rotunda.latitude<-as.numeric(geo_rotunda2$data.poll.flower.rotunda.latitude)

d.geo.rotunda2 = distm(geo_rotunda2, fun = distHaversine)
dist.geo.rotunda2 = as.dist(d.geo.rotunda2)

#abundance data frame - bray curtis dissimilarity
dist.abund.rotunda2 = vegdist(data.poll.flower.rotunda[,2:14], method = "bray")

#abundance vs geographic 
abund.geo.rotunda2  = mantel(dist.abund.rotunda2, dist.geo.rotunda2, method = "spearman", permutations = 9999, na.rm = TRUE)
abund.geo.rotunda2
```


*Aristolochia pistolochia*
```{r}
data.poll.flower.pistolochia <- filter(data.poll.mtp,plant_species %in% c("Aristolochia pistolochia")) %>% 
  filter(flower_code != "") %>%
  select(flower_code, species, nb_individuals) %>% arrange(flower_code) %>%
  pivot_wider(names_from = species, values_from = nb_individuals, values_fill = 0, values_fn = sum) %>% 
  left_join(select(data.poll.mtp,locality_code, latitude, longitude, flower_code), by="flower_code") %>% #
  distinct(flower_code, .keep_all = TRUE)

#geographic data frame - haversine distance
geo_pistolochia2 = data.frame(data.poll.flower.pistolochia$longitude, data.poll.flower.pistolochia$latitude)

geo_pistolochia2$data.poll.flower.pistolochia.longitude<-as.numeric(geo_pistolochia2$data.poll.flower.pistolochia.longitude)
geo_pistolochia2$data.poll.flower.pistolochia.latitude<-as.numeric(geo_pistolochia2$data.poll.flower.pistolochia.latitude)

d.geo.pistolochia2 = distm(geo_pistolochia2, fun = distHaversine)
dist.geo.pistolochia2 = as.dist(d.geo.pistolochia2)

#abundance data frame - bray curtis dissimilarity
dist.abund.pistolochia2 = vegdist(data.poll.flower.pistolochia[,2:7], method = "bray")

#abundance vs geographic 
abund.geo.pistolochia2  = mantel(dist.abund.pistolochia2, dist.geo.pistolochia2, method = "spearman", permutations = 9999, na.rm = TRUE)
abund.geo.pistolochia2
```

*Aristolochia clematitis*
```{r}
data.poll.flower.clematitis <- filter(data.poll.mtp,plant_species %in% c("Aristolochia clematitis")) %>% filter(flower_code != "") %>%
  select(flower_code, species, nb_individuals) %>% arrange(flower_code) %>%
  pivot_wider(names_from = species, values_from = nb_individuals, values_fill = 0, values_fn = sum) %>% 
  left_join(select(data.poll.mtp,locality_code, latitude, longitude, flower_code), by="flower_code") %>% #
  distinct(flower_code, .keep_all = TRUE)

#geographic data frame - haversine distance
geo_clematitis2 = data.frame(data.poll.flower.clematitis$longitude, data.poll.flower.clematitis$latitude)
d.geo.clematitis2 = distm(geo_clematitis2, fun = distHaversine)
dist.geo.clematitis2 = as.dist(d.geo.clematitis2)

#abundance data frame - bray curtis dissimilarity
dist.abund.clematitis2 = vegdist(data.poll.flower.clematitis[,2:11], method = "bray")

#abundance vs geographic 
abund.geo.clematitis2  = mantel(dist.abund.clematitis2, dist.geo.clematitis2, method = "spearman", permutations = 9999, na.rm = TRUE)
abund.geo.clematitis2
```


********************************************************************************
*Comparisons of floral visitors in synchronopatry*
********************************************************************************

**Data set for occupied flowers by each pollinator species**

```{r}
library(dplyr)
data.poll.mtp.1<-data.poll.mtp
data.poll.mtp.1$nb_individuals<-1 #The number of flowers occupied by each pollinator species, so the abundance of pollinators is no longer relevant
data.poll.mtp.1 <- aggregate(x = data.poll.mtp.1$nb_individuals, by = list(data.poll.mtp.1$date,data.poll.mtp.1$species,data.poll.mtp.1$locality_code, data.poll.mtp.1$flower_code,data.poll.mtp.1$plant_species), FUN=min)
colnames(data.poll.mtp.1)<-c("date","species","locality_code","flower_code","plant_species","nb_individuals") 

data.fleur.station.date <- filter(data.poll.mtp.1, species %in% list.poll) %>%
  group_by(date,locality_code, plant_species, species) %>% summarise(n=sum(nb_individuals)) %>% ungroup() %>%
  pivot_wider(names_from = species, values_from = n, values_fill = 0, values_fn = sum) %>%
  left_join(select(data.poll.mtp, date, locality_code,plant_species), by=c("date", "locality_code", "plant_species")) %>% distinct(date, locality_code, plant_species, .keep_all = TRUE) 
```

**Flowers occupied**
```{r}
syntopicf<-select(data.inspect.mtpM, date, locality_code,plant_species, nb_flowers_inspected)
syntopiccf<-full_join(syntopicf, data.fleur.station.date, by = c("date","locality_code","plant_species"))
syntopiccf[,(4:19)][is.na(syntopiccf[,(4:19)])]<-0
```

*A.rotunda & A. clematitis*
```{r}
#Filter the synchronopatric stations
SyntopicCleRot2<-filter(syntopiccf, locality_code %in% c("ES1","ME1","MA1","SA1","VA1"), nb_flowers_inspected >0)

#Sort rows where data on both species on the same day on the same site
SyntopicCleRot2<-slice(SyntopicCleRot2, -c(38,39)) # remove sampling sessions with only one species sampled
SyntopicCleRot2$date<-as.character(SyntopicCleRot2$date)

SyntopicCleRot2f<-unite(SyntopicCleRot2,date,locality_code,sep="_",remove=TRUE)
```

*A.rotunda & A.pistolochia*
```{r}
#Filter the synchronopatric stations
SyntopicRotPis2<-filter(syntopiccf, locality_code %in% c("BR2","BR1","LAM1","MU2","PO1","SG10","SG11","SG9","VF2"), nb_flowers_inspected >0)

#Sort rows where data on both species on the same day on the same site
SyntopicRotPis2<-slice(SyntopicRotPis2, -c(48,23,24,21,4,42,25))
SyntopicRotPis2$date<-as.character(SyntopicRotPis2$date)
SyntopicRotPis2f<-unite(SyntopicRotPis2,date,locality_code,sep="_",remove=TRUE)
```

**Number of flowers occupied by each fly species for each plant species in synchronopatry**

*A.rotunda & A.pistolochia*
```{r}
tapply(SyntopicRotPis2f$`Forcipomyia aristolochiae`,SyntopicRotPis2f$plant_species,sum)
tapply(SyntopicRotPis2f$`Forcipomyia monilicornis`,SyntopicRotPis2f$plant_species,sum)
tapply(SyntopicRotPis2f$`Trachysiphonella ruficeps`,SyntopicRotPis2f$plant_species,sum)
tapply(SyntopicRotPis2f$`Tricimba cincta`,SyntopicRotPis2f$plant_species,sum)
```

#Count for each pollinator species manually

>Example

```{r}
# Creation of vectors corresponding to the two categories (empty flowers/occupied flowers)
Arotsp = c(2932,174) #Arotunda
Apissp = c(3862,31) #Apistolochia

#Chisquare test
tablefa = matrix(c(Arotsp,Apissp),2,2,byrow=T)
khi_test = chisq.test(tablefa)
khi_test
```

*A.rotunda & A.clematitis*
```{r}
SyntopicCleRot2fbis<-SyntopicCleRot2f[,-(4:9)]

#Dasyhelea punctiventris
tapply(SyntopicCleRot2f$`Dasyhelea punctiventris`,SyntopicCleRot2f$plant_species,sum)
#Dasyhelea turficola
tapply(SyntopicCleRot2f$`Dasyhelea turficola`,SyntopicCleRot2f$plant_species,sum)
```

```{r}
#Forcipomyia alacris
tapply(SyntopicCleRot2f$`Forcipomyia alacris`,SyntopicCleRot2f$plant_species,sum)
#Forcipomyia aristolochiae
tapply(SyntopicCleRot2f$`Forcipomyia aristolochiae`,SyntopicCleRot2f$plant_species,sum)
#Forcipomyia knockensis
tapply(SyntopicCleRot2f$`Forcipomyia knockensis`,SyntopicCleRot2f$plant_speciesp,sum)
#Forcipomyia psilonota
tapply(SyntopicCleRot2f$`Forcipomyia psilonota`,SyntopicCleRot2f$plant_species,sum)
#Forcipomyia spCerato10
tapply(SyntopicCleRot2f$`Forcipomyia spCerato10`,SyntopicCleRot2f$plant_species,sum)
#Trachysiphonella ruficeps
tapply(SyntopicCleRot2f$`Trachysiphonella ruficeps`,SyntopicCleRot2f$plant_species,sum)

#Hapleginella laevifrons
tapply(SyntopicCleRot2f$`Hapleginella laevifrons`,SyntopicCleRot2f$plant_species,sum)
#Tricimba cincta
tapply(SyntopicCleRot2f$`Tricimba cincta`,SyntopicCleRot2f$plant_species,sum)
#Tricimba humeralis
tapply(SyntopicCleRot2f$`Tricimba humeralis`,SyntopicCleRot2f$plant_species,sum)
#Conioscinella cf mimula
tapply(SyntopicCleRot2f$`Conioscinella cf mimula`,SyntopicCleRot2f$plant_species,sum)
```

#Count for each pollinator species manually

>Example

```{r}
# Creation of vectors corresponding to the two categories (empty flowers/occupied flowers)
Arotsp2 = c(1133,0) #Arotunda
Aclemsp2 = c(1825,7) #Aclematitis

#Chisquare test
table2 = matrix(c(Arotsp2,Aclemsp2),2,2,byrow=T)
khi_test = chisq.test(table2)
khi_test
```