---
title: "S3_Script_Odours"
output: html_document
date: "2025-02-07"
---

###########################################

**Floral VOCs** 

###########################################

```{r setup, include=FALSE}
library("ChemmineR")
library("fmcsR")
vapply(c("stringr","mgcv", "RColorBrewer", "dplyr","ggplot2","tidyverse", "lme4","vegan","emmeans","compositions"), library, logical(1L),
       character.only = TRUE, logical.return = TRUE)
citation(package = "chemodiv")
```

*Important: before importing the csv file, you must have the dataset in the form of a matrix with individuals in rows and compounds in columns*

#Import datafile
```{r}
dataset<-read.csv("D5_Data_floral_odours.csv",header = T,sep = ";", dec=".")

datasetb<-dataset[,-1]
row.names(datasetb)<-dataset[,1]
```

#Convert data into proportions
```{r}
datasetc<-datasetb
datasetc$sum<-rowSums(datasetc)

datasetc[,1:90]<-(datasetc[,1:90]/datasetc$sum)*100
datasetc<-datasetc[,-90]
```

#Values below 0.1% are not taking into account (Tr)
```{r}
datasetc[datasetc < 0.1] <- 0
```

```{r}
species<-c(rep("Aristolochia pistolochia",16), rep("Aristolochia rotunda",7))
datasetc$species<-species
```

#CLR transformation of data, adding 0.1 to all values 
```{r}
clr_function <- function(x) {
  return(log1p(x = x / (exp(x = sum(log1p(x = x[x > 0]), na.rm = TRUE) / length(x = x)))))
}

min(datasetc[,1:89][datasetc[,1:89] != 0])
Chemistry.compositional <- clr_function(datasetc[,1:89] + 0.1)
```

#PCOA
```{r}
library(ape)
# PCoA
matrixbray<-vegdist(Chemistry.compositional, method="aitchison")
pcoa<-cmdscale(matrixbray, eig = TRUE)

speciescol<-c(rep("#FF5722",16), rep("#C0CA33",7))
ordiplot(pcoa,type="points")
points (pcoa$points,col = speciescol, pch=c(18,18,18,18,18,18,18,18,18,18,18,18,18,18,18,18,17,17,17,17,17,17,17), cex=1.5)
title("PCoA_Aristolochia")

barplot(pcoa$eig,col="black", ylab = 'eigenvalues')
(pcoa$eig[1]/sum(pcoa$eig))*100
(pcoa$eig[2]/sum(pcoa$eig))*100
```

*PLS-DA on compositional data*
```{r}
library(Hotelling)
library(ade4)
library(vegan)
library(pls)
library(RVAideMemoire)
```

#We fit the PLS-DA model:
```{r}
PPLSDA_dummy2 <- dummy(datasetc$species)

rowSums(datasetc[1:23,1:89])
colSums(datasetc[1:23,1:89])

library(compositions)
données3bis<- clr_function(datasetc[1:23,1:89]+ 0.1)
Chemistry3bis<-as.matrix(données3bis[,1:89])

PPLSDAbis <- cppls(PPLSDA_dummy2~Chemistry3bis)
```

```{r}
#PPLSDA
MVA.cmv(Chemistry3bis,factor(datasetc$species[1:23]),model="PPLS-DA",
crit.inn="NMC",ncomp=2)

MVA.test(Chemistry3bis,factor(datasetc$species[1:23]),model="PPLS-DA",
cmv=TRUE,ncomp=2)
```

```{r}
MVA.synt(PPLSDAbis)
MVA.plot(PPLSDAbis,xax=1, yax=2, fac=datasetc$species[1:23],drawextaxes=FALSE,pch=c(15,17), cex= 1.5, col=c("#FF5722","#C0CA33"), main="PPLS-DA")
```

*PERMANOVA*
```{r}
library(vegan)
library(RVAideMemoire)
ado<-adonis2(as.matrix(Chemistry.compositional) ~ datasetc$species, permutations = 999, method = "aitchison" , by = "onedf")
ado

pairwise.perm.manova(vegdist(as.matrix(Chemistry.compositional),"aitchison"),datasetc$species,p.method = "fdr")
```

###########################################

**Behavioural attraction** 

###########################################

#Import data
```{r}
behaviour<-read.csv("D6_McPhail_traps_odourattractant.csv",header = T, row.names = NULL,sep = ";")
```

#Visualize data
```{r}
behaviour2<-behaviour
length(unique(behaviour2$trap))

za<-tapply(behaviour2$trap, behaviour2$odour, n_distinct)
za

z<-data_frame(tapply(behaviour2$specimen_sample, behaviour2$odour, n_distinct))
x<-sort(behaviour2$odour)
rownames(z)<-unique(x)
z<-rename(z, "Traps" = `tapply(behaviour2$specimen_sample, behaviour2$odour, n_distinct)`)
```

```{r}
library(ggplot2)

ggplot(behaviour2) +
 aes(x = odour, y = number, fill = family) +
 geom_col() +
 scale_fill_viridis_d(option = "viridis", 
 direction = 1) +
 coord_flip() +
 theme_gray() +
 theme(axis.text.y = element_text(face = "bold", size = 15L), 
 axis.text.x = element_text(face = "bold", size = 15L))
```

```{r}
ggplot(behaviour2) +
 aes(x = odour, y = nb, fill = espece) +
 geom_col() +
 scale_fill_viridis_d(option = "viridis", 
 direction = 1) +
 coord_flip() +
 theme_gray() +
 theme(axis.text.y = element_text(face = "bold", size = 15L), 
 axis.text.x = element_text(face = "bold", size = 15L))

ggplot(behaviour2) +
 aes(x = odour, y = nb, fill = sexe) +
 geom_col() +
 scale_fill_viridis_d(option = "viridis", 
 direction = 1) +
 coord_flip() +
 theme_gray() +
 theme(axis.text.y = element_text(face = "bold", size = 15L), 
 axis.text.x = element_text(face = "bold", size = 15L))
```

#Total number of flies attracted and by family
```{r}
sum(behaviour2$number)
tapply(behaviour2$number, behaviour2$family, sum)
```

#F. monilicornis
```{r}
forcip<-subset(behaviour2, behaviour2$species=="Forcipomyia monilicornis")
sum(forcip$number)
length(unique(forcip$trap))
forcip


chloro<-subset(behaviour2, behaviour2$family=="Chloropidae")
sum(chloro$number)
length(unique(chloro$trap))
chloro 
```